---
title: "ICM Curriculum Progress"
output: html_document
---

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

## docker run -d -p 4445:4444 selenium/standalone-chrome

## Although really now you just need to run 'docker start 7e8eecaab437'
## docker ps

source("set_up_ficm_curriculum.R")
source("ficm_curriculum.R")
```

```{r filter_table, include=FALSE}
curriculum_red_table <- curriculum %>%
  filter(circle == "Red Circle") %>%
  select(competency) %>%
  knitr::kable()

curriculum_green_table <- curriculum %>%
  filter(circle == "Green Circle") %>%
  select(competency) %>%
  knitr::kable()

competency_total <- curriculum %>% nrow()
competency_red <- curriculum %>% filter(circle == "Red Circle") %>% nrow()
competency_green <- curriculum %>% filter(circle == "Green Circle") %>% nrow()

```

```{r export_table, message=FALSE, warning=FALSE, include=FALSE}
today <- Sys.Date()
today <- str_replace_all(today, "-", "_")
file_name <- str_c(today, "-red_competency_table.csv", sep = "")

curriculum_red_table_export <- curriculum %>%
  filter(circle == "Red Circle") %>%
  select(competency)

write_excel_csv(curriculum_red_table_export, file_name)
```
  
```{r load case_packages, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
source("ficm_thirty_cases.R")
```

```{r filter_another_table, include=FALSE}
thirtycases_red_table <- thirtycases %>%
  filter(circle == "Red Circle") %>%
  select(case) %>%
  knitr::kable()

thirtycases_green_table <- thirtycases %>%
  filter(circle == "Green Circle") %>%
  select(case) %>%
  knitr::kable()

thirtycases_total <- thirtycases %>% nrow()
thirtycases_red <- thirtycases %>% filter(circle == "Red Circle") %>% nrow()
thirtycases_green <- thirtycases %>% filter(circle == "Green Circle") %>% nrow()

```

```{r export_case_table, message=FALSE, warning=FALSE, include=FALSE}
today <- Sys.Date()
today <- str_replace_all(today, "-", "_")
file_name <- str_c(today, "-red_cases_table.csv", sep = "")

cases_red_table <- thirtycases %>%
  filter(circle == "Red Circle") %>%
  select(case)

write_excel_csv(cases_red_table, file_name)
```

# Summary

```{r table, echo=FALSE, fig.height=5, fig.width=20, message=FALSE, warning=FALSE, paged.print=FALSE}
summary <- tibble(Area = c("Competencies", "Cases", "Competencies", "Cases"),
          Numbers = c(competency_red, 10 - thirtycases_green, competency_green, thirtycases_green),
          Colours = c("Red", "Red", "Green", "Green"))

colours_portfolio <- c("#39F224", "#F33030")

summary %>%
  ggplot(aes(Area, Numbers, fill = Colours)) +
  geom_bar(stat = "identity", position = "fill") +
  coord_flip() +
  theme_minimal() +
  scale_fill_manual(values = colours_portfolio) +
  labs(title = "Progress So Far",
       xlab = "Proportion",
       ylab = "Area") +
  theme(legend.position = "none")

```

# Competencies

## 游릭vs游댮

## There are `r competency_total` total competencies

### So far I have `r competency_green` signed off

### I need to get `r competency_red` more signed off

## 游댮 To Complete:

`r curriculum_red_table`

## 游릭 Completed:

`r curriculum_green_table`

# Cases

## 游릭vs游댮

## There are `r thirtycases_total` total competencies

### So far I have `r thirtycases_green` signed off

### I need to get `r 10 - thirtycases_green` more signed off 

## 游댮 To Complete:

`r thirtycases_red_table`

## 游릭 Completed:

`r thirtycases_green_table`
